This is an example of article title

### 2025-10-31 paper/paper.tex
Add a metric Lie group, fine tuning of code env would be neccessary.

\subsection{A Lie group for numerical verification}

@@

For all three representations, one can access the component semantically by writing \verb|g[G, :Rotation]| and \verb|g[G, :Translation]|, which works independent of the representation used.

{\color{red}TODO: Check whether there are details for other Lie groups that should be mentioned here.}

>>>>

\subsection{Decorators for Lie groups}

The decorator pattern is used within the \verb|JuliaManifolds| ecosystem to add or modify existing funtionality.
For Lie groups there are currently two such decorators available

\subsubsection*{Specifying a different inner product}

By implementing \verb|inner(|$\frak g$\verb|, X, Y)| and \verb|norm(|$\frak g$\verb|, X)| for a Lie algebra $\frak g$\verb| = LieAlgebra(G)|,
the Lie group \verb|G| is equipped with a certain inner product on the Lie algebra and hence on all tangent spaces to the Lie group.
This is an implicit choice of a default metric on the Lie group, that is considered the default thereafter.

If more than one metric is used in applications, a second metric can be introduced
by wrapping the Lie group into a \verb|MetricLieGroup|, i.e.\ \verb|G2 = MetricLieGroup(G, m::M)|, where \verb|M| has to be a subtype of
\verb|AbstractMetric| available from \verb|Manifolds.jl|\footnote{where the analogously a manifold of type~\texttt{MetricManifold} is defined.}.
All functions unrelated to the metric are forwarded from \verb|G2| to \verb|G|, while all functions
related to the inner product have to be specified for \verb|G2| anew.

\subsubsection*{Adding numerical validation to a Lie group}

@@

For all three representations, one can access the component semantically by writing \verb|g[G, :Rotation]| and \verb|g[G, :Translation]|, which works independent of the representation used. This allows to implement algorithgms wotking on \(\mathrm{SE}(n)\) indepentently of the chosen representation.
